Machine Learning Methods for Discourse Segmentation of Communications in E-Mail Based Behavioral Interventions

### 2018-08-07 paper-amia-summit-2018/manuscript.tex
update introduction

\begin{enumerate}
\item Emails are unstructured text that contains informal information exchange in a non-traditional format. For example, an e-Coach usually responds to several queries of a patient in one email. However, a provider utterance of MI transcript denotes a particular response for a query of a patient during a traditional MI interview session, which involve a dialogue between a provider and a patient. 
\item Discourse segments in e-Coaching emails do not necessarily correspond to sentences or collection of sentences. One sentence can be segmented into multiple MI behavior fragments. On the other hand, an MI behavior may comprise several sentences.
\end{enumerate}

>>>>

\begin{enumerate}
\item Emails are unstructured text that contains informal information exchange in a non-traditional format. For example, an e-Coach usually responds to a patient with their various concerns in one email. On the other hand, a traditional communication exchange involves a dialogue between a provider and a patient, where a provider addresses a particular concern of a patient in one utterance during the MI interview session. 
\item Discourse segments in e-Coaching emails do not necessarily correspond to sentences or collection of sentences. One sentence can be segmented into multiple MI behavior fragments. On the other hand, an MI behavior may comprise several sentences.
\end{enumerate}
